Desert Ant Behaviour: Simulating Movement and Navigation

### 2011-12-15 documentation/report.tex
whitespace inserted

\begin{abstract}
This paper is the final result of the course {\sc Modeling Social Systems with MATLAB\texttrademark} which aimed to offer an insight into the MATLAB\texttrademark programming language and to use said language to model social systems with various approaches. The timeframe of the course is one semester. \\
In this paper we will try to show how to replicate the behaviour of desert ants in a MATLAB\texttrademark simulation. Furthermore we will discuss our results and compare them to experimental results obtained by biologists.
\end{abstract}

@@

However, these algorithms are modeling the behaviour of forest ants of the western hemisphere, which is not similar to the behaviour of desert in terms of choosing a good path and searching for food. Since we are studying desert ants we had to take a different approach. Desert ants rely much more heavily on the few landmarks they find in their environment and less on pheromone tracks other ants have left before them, which is what forest ants do. They make use of a path integraton which enables them to track their position in reference to where they started the journey, most likely the nest.\\\\
Results of interest are:
\begin{itemize}
\item How optimized and efficent is navigation by vectors
\item How well do the ants learn in the course of repeated journey towards the food and back
\item Of course we were as well motivated to improve our knowledge of MATLAB\texttrademark
\end{itemize}

@@

\begin{table}[h!]
\centering
\begin{tabular}{lll}
   \cmidrule[1pt]{2-3}
   & Color in png-file & Color in MATLAB\texttrademark \\
   \midrule
Obstacle & black & red \\ \midrule
Nest & green & black circle \\ \midrule
Feeder & blue & black cross \\ \midrule
Landmark & turquoise & blue circle \\
\bottomrule  
\end{tabular}
\caption{Color values and their meaning}
\label{tab1}
\end{table}

>>>>

\begin{abstract}
This paper is the final result of the course {\sc Modeling Social Systems with MATLAB\texttrademark} which aimed to offer an insight into the MATLAB\texttrademark\ programming language and to use said language to model social systems with various approaches. The timeframe of the course is one semester. \\
In this paper we will try to show how to replicate the behaviour of desert ants in a MATLAB\texttrademark\ simulation. Furthermore we will discuss our results and compare them to experimental results obtained by biologists.
\end{abstract}

@@

However, these algorithms are modeling the behaviour of forest ants of the western hemisphere, which is not similar to the behaviour of desert in terms of choosing a good path and searching for food. Since we are studying desert ants we had to take a different approach. Desert ants rely much more heavily on the few landmarks they find in their environment and less on pheromone tracks other ants have left before them, which is what forest ants do. They make use of a path integraton which enables them to track their position in reference to where they started the journey, most likely the nest.\\\\
Results of interest are:
\begin{itemize}
\item How optimized and efficent is navigation by vectors
\item How well do the ants learn in the course of repeated journey towards the food and back
\item Of course we were as well motivated to improve our knowledge of MATLAB\texttrademark\
\end{itemize}

@@

\begin{table}[h!]
\centering
\begin{tabular}{lll}
   \cmidrule[1pt]{2-3}
   & Color in png-file & Color in MATLAB\texttrademark\ \\
   \midrule
Obstacle & black & red \\ \midrule
Nest & green & black circle \\ \midrule
Feeder & blue & black cross \\ \midrule
Landmark & turquoise & blue circle \\
\bottomrule  
\end{tabular}
\caption{Color values and their meaning}
\label{tab1}
\end{table}
